Clause size reduction with all-UIP Learning

### 2020-02-24 paper.tex
fix bib file

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & $\allUip$ attempt rate & $\allUip$ success rate  \\ 
%\hline
%$\MapleIUIPPure$ & 16.1\% & 43.4\% \\ 
%\hline
%$\MapleIUIMin$ & 28.8\% & 59.3\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Compare $\allUipPure$ and $\allUipMin$ i-uip attempt rate and success rate. %$\allUipMin$ scheme attempted $\allUip$ more frequently, and it is more likely to %successfully produce smaller $C_i$ clause .}
%\label{fig:t2}
%\end{figure}
\subsubsection{Proof Reduction with $\allUip$}
A learning scheme yields smaller clauses (lemmas) may construct smaller causal proofs. For
UNSAT instances, we additionally compare the size of the optimized DRAT proof from $\allUipPure$, $\allUipMin$ and 1-UIP schemes. We used DART-trim \cite{wetzler2014drat} with 10000 second timeout to check and optimize every DRAT proof once \footnote{Applying DART-trim multiple times can further reduce the proof size until fix-point, but the full optimization is time consuming and impractical for our experiments.}.

@@

\subsubsection{$\allUip$ on Modern SAT solvers}
To validate $\allUip$ as practical learning schemes on modern SAT
solvers, we re-implement $\allUip$ on the winners of 2017, 2018 and 2019
SAT Race\cite{luo2017effective,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT} and $\expSAT$\cite{MdSolimul2019expMalpe} ($\expSATShort$). $\expSATShort$
is a top ten solver from 2019 SAT race which uses random walk
simulation to help branching. We chose $\expSATShort$ because 1) it is
a top solver in the 2019 SAT Race without using chronological
backtracking; 2) the random walk simulation 
branching heuristic is different from local branching heuristic (VSIDS and LRB) that we have considered,
hence it is in the blind spot of $\allUip$.
we compare the base 1-UIP learning scheme against $\allUipPure$,
$\allUipMin$ and the top two $\allUip$ variants, $\allUipAct$ and
$\allUipIn$, on the SAT Race 2019 main track benchmark. We report
solved instances, PAR-2 score and the average clause size.

>>>>

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & $\allUip$ attempt rate & $\allUip$ success rate  \\ 
%\hline
%$\MapleIUIPPure$ & 16.1\% & 43.4\% \\ 
%\hline
%$\MapleIUIMin$ & 28.8\% & 59.3\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Compare $\allUipPure$ and $\allUipMin$ i-uip attempt rate and success rate. %$\allUipMin$ scheme attempted $\allUip$ more frequently, and it is more likely to %successfully produce smaller $C_i$ clause .}
%\label{fig:t2}
%\end{figure}
\subsubsection{Proof Reduction with $\allUip$}
A learning scheme yields smaller clauses (lemmas) may construct smaller causal proofs. For
UNSAT instances, we additionally compare the size of the optimized DRAT proof from $\allUipPure$, $\allUipMin$ and 1-UIP schemes. We used DART-trim \cite{DBLP:conf/sat/WetzlerHH14} with 10000 second timeout to check and optimize every DRAT proof once \footnote{Applying DART-trim multiple times can further reduce the proof size until fix-point, but the full optimization is time consuming and impractical for our experiments.}.

@@

\subsubsection{$\allUip$ on Modern SAT solvers}
To validate $\allUip$ as practical learning schemes on modern SAT
solvers, we re-implement $\allUip$ on the winners of 2017, 2018 and 2019
SAT Race\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT} and $\expSAT$\cite{MdSolimul2019expMalpe} ($\expSATShort$). $\expSATShort$
is a top ten solver from 2019 SAT race which uses random walk
simulation to help branching. We chose $\expSATShort$ because 1) it is
a top solver in the 2019 SAT Race without using chronological
backtracking; 2) the random walk simulation 
branching heuristic is different from local branching heuristic (VSIDS and LRB) that we have considered,
hence it is in the blind spot of $\allUip$.
we compare the base 1-UIP learning scheme against $\allUipPure$,
$\allUipMin$ and the top two $\allUip$ variants, $\allUipAct$ and
$\allUipIn$, on the SAT Race 2019 main track benchmark. We report
solved instances, PAR-2 score and the average clause size.
